### 2015-03-28 zoldatoff/tex/text retrieval/title.tex
Лекции по курсу Text Retrieval
Лекции с 1-й по 5-ю

{\LARGE PATTERN DISCOVERY \\ IN \\[0.3\baselineskip] DATA MINING}\\[0.2\baselineskip] % Title

@@

\scshape % Small caps
Concepts and challenges in pattern discovery and analysis. \\ 
Pattern evaluation, mining and classification \\[\baselineskip] % Tagline(s) or further description

@@

Course author:\\[\baselineskip]
{\Large JIAWEI HAN}\\[\baselineskip]

>>>>

{\LARGE TEXT RETRIEVAL \\ AND \\[0.3\baselineskip] SEARCH ENGINES}\\[0.2\baselineskip] % Title

@@

\scshape % Small caps
The basic concepts, principles, and the major techniques in text retrieval,\\ 
which is the underlying science of search engines. \\[\baselineskip] % Tagline(s) or further description

@@

Course author:\\[\baselineskip]
{\Large ChengXiang Zhai}\\[\baselineskip]
